\documentclass[stdletter]{newlfm}
\namefrom{Stanley and Hsiao-Chi Tzeng} \addrfrom{\parbox{2in}{847 San Rafael St.\\ Davis, CA}}
\begin{document}
\closeline{Sincerely yours,} \greetto{To Whom It May Concern:}
\begin{newlfm}
This is the package that contains the form I-130 Petition for Alien Relative and its supplemental material.  In this package you will find:
\begin{itemize}

\item One form I-130 Petition for Alien Relative filled out by Stanley with a cover letter.
\item One photocopy of Stanley's birth certificate.
\item One official copy of Stanley and Angel's marriage license.
\item One form G-325A filled out by Stanley.
\item One check with amount \$420.
\item For the bonafide of the marriage:
\begin{itemize}
\item Six affidavits affirming the marriage.  These affidavits are from our family, friends and mentors who are all US Citizens and have known us for a long time.
\item Two letters from Citibank showing our joint bank account.  There are two letters because Citibank did an account lookup on my wife and me and each lookup is one letter.  Nonetheless, the account number on both letters are identical.
\item One passport photo of Stanley.
\end{itemize}

\end{itemize}

Both packages include their respective cover letters detailing what is inside each package.  Should there be any questions, please do not hesitate to contact us via e-mail stzeng@ucdavis.edu or by phone at 650-996-9847.  Thank you once again and we look forward to hearing from you soon.
\end{newlfm}
\end{document}