\documentclass[stdletter]{newlfm}
\namefrom{Stanley and Hsiao-Chi Tzeng} \addrfrom{\parbox{2in}{847 San Rafael St.\\ Davis, CA}}
\begin{document}
\closeline{Sincerely yours,} \greetto{To Whom It May Concern:}
\begin{newlfm}
This is the package that contains the form I-485 Application to Register Permanent Residence or Adjust Status for Hsiao-Chi (Angel) Tzeng and its supplemental material.  In this package you will find:
\begin{itemize}

\item One completed I-485 Application to Register Permanent Residence form or Adjust Status filled out by Angel Tzneg.
\item One completed I-693 Report of Medical Examination and Vaccination Record form filled out by Angel and Dr. Zhang in Dixon Family Practice in Dixon, CA.
\item One completed I-765 Application for Employment Authorization form with Angel's I-20 endorsed by UC Davis.  
\item One completed I-864 Affidavit of Support form filled out by Stanley Tzeng.  This form also has a cover letter to explain what material is included.
\item One form G-325A Biographic Information filled out by Angel Tzeng.
\item One copy of Angel's residency information in Taiwan.  This is the Taiwanese equivalent of the most up-to-date birth certificate.
\item One official copy of our marriage certificate.
\item Two passport size photos of Angel Tzeng.
\item One check of \$985 for the filing fee.



\end{itemize}

Should there be any questions, please do not hesitate to contact us via e-mail stzeng@ucdavis.edu or by phone at 650-996-9847.  Thank you once again and we look forward to hearing from you soon.
\end{newlfm}
\end{document}